---
title: "How to Use EDArumour"
author: "Soveatin Kuntur"
date: "2025-04-04"
output: html_document
---

# 📦 EDArumour Package

The `EDArumour` package helps explore and analyze rumor-related text data.\
It includes functions for counting words, analyzing text patterns, and visualizing the results.

## 🔧 Functions Included

-   `runEDA()` – Analyze message length, word count, and question marks
-   `plot.eda_result()` – Draw boxplots comparing rumor vs non-rumor texts
-   `countWords()` – Count how many words are in each message

🔗 GitHub: <https://github.com/kunturs/arp-lab02>

------------------------------------------------------------------------

## 📥 Load Package and Dataset

```{r setup}
library(EDArumour)
data(pheme)
```

```{r preview-clean, message=FALSE}
library(DT)
DT::datatable(
  head(pheme, 5),
  options = list(
    dom = 't'  # Only show the table (no search box, no pagination, no dropdown)
  ),
  caption = "First 5 Rows of the PHEME Dataset"
)
```

## Run Text Analysis

```{r setup}
eda <- runEDA(pheme)
```

##Show the result 

```{r show-eda-dt}
DT::datatable(
  head(eda$data, 5),
  options = list(dom = 't'),
  caption = "First 5 Rows of EDA Results"
)
```

## Run Plot

```{r setup}
plot(eda)

```

## 📊 Boxplots from EDA

```{r eda-plot, fig.align='center', fig.width=7, fig.height=5}
plot(eda)
```

## Count words
```{r}
texts <- c("How are you?", "This is R.", "Exploratory Data Analysis!")
countWords(texts)
```
