---
title: "How to Use EDArumour"
author: "Soveatin Kuntur"
date: "2025-04-04"
output:
  html_document: default
  pdf_document: default
---

# 📦 EDArumour Package

The `EDArumour` package helps explore and analyze rumor-related text data.\
It includes functions for counting words, analyzing text patterns, and visualizing the results.

## 🔧 Functions Included

-   `runEDA()` – Analyze message length, word count, and question marks
-   `plot.eda_result()` – Draw boxplots comparing rumor vs non-rumor texts
-   `countWords()` – Count how many words are in each message

🔗 GitHub: <https://github.com/kunturs/arp-lab02>

------------------------------------------------------------------------

## 📥 Load Package and Dataset

```{r load-package}
library(ggplot2)
library(gridExtra)
library(EDArumour)  
data(pheme)
eda <- runEDA(pheme)
```

```{r preview-clean, eval = knitr::is_html_output()}
library(DT)
DT::datatable(
  head(pheme, 5),
  options = list(
    dom = 't'  # Only show the table (no search box, no pagination, no dropdown)
  ),
  caption = "First 5 Rows of the PHEME Dataset"
)
```

## Run Text Analysis

```{r text-analysis}
eda <- runEDA(pheme)
```
```{r plot-method}
plot.eda_result <- function(x, ...) {
  stopifnot(inherits(x, "eda_result"))
  df <- x$data

  p1 <- ggplot2::ggplot(df, ggplot2::aes(x = label, y = text_length, fill = label)) +
    ggplot2::geom_boxplot() +
    ggplot2::theme_minimal() +
    ggplot2::labs(title = "Text Length by Rumor Label", x = "", y = "Characters") +
    ggplot2::theme(legend.position = "none")

  p2 <- ggplot2::ggplot(df, ggplot2::aes(x = label, y = word_count, fill = label)) +
    ggplot2::geom_boxplot() +
    ggplot2::theme_minimal() +
    ggplot2::labs(title = "Word Count by Rumor Label", x = "", y = "Words") +
    ggplot2::theme(legend.position = "none")

  gridExtra::grid.arrange(p1, p2, ncol = 2)
}
```

##Show the result 

```{r show-eda-dt}
DT::datatable(
  head(eda$data, 5),
  options = list(dom = 't'),
  caption = "First 5 Rows of EDA Results"
)
```

##Check class

```{r check-class}
class(eda)

````


## 📊 Boxplots from EDA

```{r eda-plot, fig.align='center', fig.width=7, fig.height=5}
#install.packages("gridExtra")
library(gridExtra)
plot(eda)
```

## Count words
```{r func}
texts <- c("How are you?", "This is R.", "Exploratory Data Analysis!")
countWords(texts)
```

